---
title: "Democratic Candidate Fact Checks Transitional App"
resource_files:
- .httr-oauth
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: cerulean
---

```{r setup, include=FALSE}

library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(googlesheets)
library(kableExtra)
library(leaflet)
# library(ggmap)
library(RColorBrewer)
library(htmlwidgets)
library(htmltools)
library(tigris)
options(tigris_class = "sf")

#use saved version of data (for now during development)
# fcheck <- readRDS("saved_versions/fcheck_saved.rds")


#import live version from google sheet
#register google sheet
mykey <- Sys.getenv("CNNfcheck_KEY")
fc2020 <- gs_key(mykey)

#list worksheets in the google sheet
gs_ws_ls(fc2020)

#read in all the data in a sheet
fcheck <- fc2020 %>% 
  gs_read(ws = "Sheet1") %>% 
  clean_names() 

names(fcheck)

#set formatting of certain columns
fcheck <- fcheck %>% 
  mutate(
    date = mdy(date),
    candidate = str_trim(str_to_upper(candidate)),
    spectrum_of_truth = str_trim(str_to_upper(spectrum_of_truth)),
    # claim = str_trim(str_to_upper(claim)),
    # fact_check = str_trim(str_to_upper(fact_check)),
    subject = str_trim(str_to_upper(subject)),
    source = str_trim(str_to_upper(source))
  )


fcheck <- fcheck %>% 
  mutate(
    candidate = as.factor(candidate),
    source = as.factor(source),
    spectrum_of_truth = as.factor(spectrum_of_truth),
    subject = as.factor(subject)
  )

#convert link to html hyperlink format
fcheck$link <- paste0("<a href='", fcheck$link, "' target='_blank'>", fcheck$link, "</a>")

#save version with ALL records (CNN and non-CNN alike)
fcheck_all <- fcheck

#filter for just CNN
fcheck <- fcheck %>% 
  filter(source == "CNN")


#number of candidates
cands_included <- fcheck %>% 
  count(candidate) %>% 
  nrow()

#number of subjects
subjects_included <- fcheck %>% 
  count(subject) %>% 
  nrow()


# set time object set to EST
d <- Sys.Date()
# d <- .POSIXct(d, "EST")
  
t <- Sys.time()
t <- .POSIXct(t, "EST")

```


Searchable Database (CNN Only)
===================================== 
Published and Triad-approved CNN fact checks through `r format(d, format="%b %d")`. To **filter** a column, click on the box above that column. To **sort**, click on the arrows by the column names. To **search globally** by keywords, use the search box on the right. 
(Last updated on `r format(t, format="%B %d %I:%M %p %Z")`)


Row 
-----------------------------------------------------------------------

### {data-width=800}

```{r}

#searchable table

fcheck_table <- fcheck %>% 
  select(candidate,
         date,
         spectrum_of_truth,
         subject,
         claim,
         fact_check,
         link) %>% 
  arrange(desc(date))

datatable(fcheck_table, 
          rownames = FALSE, 
          filter = "top",
          escape = FALSE,
          options = list(searchHighlight = TRUE)) %>% 
  formatDate('date', 'toDateString') %>% 
  formatStyle('candidate', fontWeight = 'bold')


```


Summary Counts (CNN Only)
=====================================


Row {data-height=200}
-----------------------------------------------------------------------

### Total CNN Fact Checks

```{r}

tot <- nrow(fcheck)

valueBox(tot, icon = "fa-pencil", color = "lightblue")


```

### Total candidates included

```{r}

valueBox(cands_included, icon = "fa-users", color = "#A8E9A8")


```

### Total number of subjects

```{r}

valueBox(subjects_included, icon = "fa-book", color = "#f4a8a7")


```


Row {data-height=800}
-----------------------------------------------------------------------


### Totals by truth spectrum

```{r}

byspectrum <- fcheck %>% 
  count(spectrum_of_truth) 


d <- ggplot(data = byspectrum, aes(x = reorder(spectrum_of_truth, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "lightblue") +
  # coord_flip() +
  theme_minimal()

d2 <- d + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

dd <- ggplotly(d2)

dd_nomenu <- dd %>% config(displayModeBar = FALSE)
dd_nomenu

# ggplot(corr.m, aes(x = reorder(miRNA, -value), y = value, fill = variable)) + 
#   geom_bar(stat = "identity")

```


### Candidates with most fact checks

```{r}

bycand <- fcheck %>% 
  count(candidate) %>% 
  arrange(desc(n)) %>% 
  head() %>% 
  ungroup()


e <- ggplot(data = bycand, aes(x = reorder(candidate, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#A8E9A8") +
  # coord_flip() +
  theme_minimal()

e2 <- e + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ee <- ggplotly(e2)

ee_nomenu <- ee %>% config(displayModeBar = FALSE)
ee_nomenu


```


<!-- Row  -->
<!-- ----------------------------------------------------------------------- -->

### Most common subjects

```{r}

bysubject <- fcheck %>% 
  count(subject) %>% 
  arrange(desc(n)) %>% 
  head() %>% 
  ungroup()


e <- ggplot(data = bysubject, aes(x = reorder(subject, -n), y = n)) +
  geom_col(
    # color = "#848484",
    fill = "#f4a8a7") +
  # coord_flip() +
  theme_minimal()

e2 <- e + labs(x ="", y = "") +
  theme(plot.title = element_text(hjust = 0.5)) +
  # scale_fill_manual(values=cbPalette) +
  theme(legend.title=element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ee <- ggplotly(e2)

ee_nomenu <- ee %>% config(displayModeBar = FALSE)
ee_nomenu


```



Searchable Database (All Sources)
===================================== 
Published fact checks from a curated list of fact-checking and news organization sites. This includes CNN itself but also ones like Politifact, the NYT, AP, etc. (Please consult the fact-checking team and/or the Row before including any non-CNN items in your public reporting.)
To **filter** a column, click on the box above that column. To **sort**, click on the arrows by the column names. To **search globally** by keywords, use the search box on the right. 


Row 
-----------------------------------------------------------------------

### {data-width=800}

```{r}

#searchable table

fcheck_all_table <- fcheck_all %>% 
  select(source,
         candidate,
         date,
         spectrum_of_truth,
         subject,
         claim,
         fact_check,
         link) %>% 
  arrange(desc(date))

datatable(fcheck_all_table, 
          rownames = FALSE, 
          filter = "top",
          escape = FALSE,
          options = list(searchHighlight = TRUE)) %>% 
  formatDate('date', 'toDateString') %>%  
  formatStyle('source', color = 'darkred') %>% 
  formatStyle('candidate', fontWeight = 'bold')


```




Questions?
=====================================

Row 
-----------------------------------------------------------------------
If you have any questions about these fact checks, please give a shout to Aaron.Kessler@cnn.com, Matthew.Philips@cnn.com or Cat.Gloria@cnn.com. 
